---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setoptions, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE,tidy=TRUE)
```

## Loading and preprocessing the data

```{r}
unzip("activity.zip")
walkdata <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
```{r}
totalSteps <- aggregate(steps~date, data=walkdata, sum, na.rm=TRUE)
hist(totalSteps$steps)

meanSteps <- mean(totalSteps$steps)
medianSteps <- median(totalSteps$steps)
```

* The mean of the total number of steps taken per day is: `r sprintf("%.1f",meanSteps)`
* The median of the total number of steps taken per day is: `r medianSteps`


## What is the average daily activity pattern?
```{r}
stepsToInterval <- aggregate(steps~interval, data=walkdata, mean, na.rm=TRUE)
plot(steps~interval,data=stepsToInterval,type="l")
```

```{r}
max5Minute <- stepsToInterval[which.max(stepsToInterval$steps),]$interval
```

* The 5-minute interval which on average across all the days in the dataset, contains the maximum number of steps is: `r max5Minute`


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
