---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
  word_document: default
---

```{r setoptions, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE,tidy=TRUE)
```

## Loading and preprocessing the data

```{r}
unzip("activity.zip")
walkdata <- read.csv("activity.csv")
```


## What is the mean total number of steps taken per day?
```{r}
totalSteps <- aggregate(steps~date, data=walkdata, sum, na.rm=TRUE)
hist(totalSteps$steps)

meanSteps <- mean(totalSteps$steps)
medianSteps <- median(totalSteps$steps)
```

* The mean of the total number of steps taken per day is: `r sprintf("%.1f",meanSteps)`
* The median of the total number of steps taken per day is: `r medianSteps`


## What is the average daily activity pattern?
```{r}
stepsToInterval <- aggregate(steps~interval, data=walkdata, mean, na.rm=TRUE)
plot(steps~interval,data=stepsToInterval,type="l")
```

```{r}
max5Minute <- stepsToInterval[which.max(stepsToInterval$steps),]$interval
```

* The 5-minute interval which on average across all the days in the dataset, contains the maximum number of steps is: `r max5Minute`


## Imputing missing values
```{r}
totalMissing <- sum(is.na(walkdata$steps))
```
* Total number of missing values in the dataset: `r totalMissing`

```{r results="hide"}
## Find the unique time slots:
allTimeSlots <- unique(walkdata$interval)
newdata <- walkdata

## Set missing data to the average number of steps for that time slot
## where there is not missing data
## This strategy is the mean for that 5-minute interval
setMissingData <- function(timeSlot) {
    newdata[which(walkdata$interval==timeSlot & is.na(walkdata$steps)), ]$steps <<- 
        mean(walkdata[which(walkdata$interval==timeSlot & !is.na(walkdata$steps)), ]$steps)
}

lapply(allTimeSlots, setMissingData)
```

```{r}
totalNewSteps <- aggregate(steps~date, data=newdata, sum, na.rm=TRUE)
hist(totalNewSteps$steps)

meanNewSteps <- mean(totalNewSteps$steps)
medianNewSteps <- median(totalNewSteps$steps)
```

* The imputed mean of the total number of steps taken per day is: 
    `r sprintf("%.1f",meanNewSteps)`
* The imputed median of the total number of steps taken per day is: 
    `r sprintf("%.1f",medianNewSteps)`


## Are there differences in activity patterns between weekdays and weekends?
